Figures

### 2019-06-30 figures/02_hierarchical_demo.Rmd
toward a colorless hierarchical demo

cowplot::plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = colors, levels(hu4$n_cat)),
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```

>>>>

cowplot::plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme_cowplot() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP (ug/L)")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
    scale_color_manual(values = rep("black", 26)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = rep("black", 5)),
  rel_heights = c(0.6, 1), labels = "AUTO"
)
```
